[![Build Status](https://travis-ci.com/smilesun/rlR.svg?branch=master)](https://travis-ci.com/smilesun/rlR)
[![Coverage Status](https://coveralls.io/repos/github/smilesun/rlR/badge.svg?branch=master)](https://coveralls.io/github/smilesun/rlR?branch=master)
[![Build status](https://ci.appveyor.com/api/projects/status/d0oyb358bh3e8r7r?svg=true)](https://ci.appveyor.com/project/smilesun/rlr)

# rlR: Deep Reinforcement learning in R

## Installation
```{r eval = FALSE}
devtools::install_github("smilesun/rlR")
```
or 

```{r eval = FALSE}
devtools::install_github("smilesun/rlR", dependencies = TRUE)
```
To run the examples,  you need to have Python3 Package `tensorflow-1.8.0`, `keras-2.1.6`, `gym-0.10.5` installed in the **same** python package path. Other versions might also work but not tested.

If not, install the above three python packages or:

For Unix user
- Ensure that you have **either** of the following available
  - Python3 Virtual Environment: `{python eval=F}pip install virtualenv`
  - Anaconda
- Install dependencies through `{r eval=F} rlR::installDep2SysVirtualEnv(gpu = FALSE)` if you have python virtualenv available or `{r eval=FALSE} rlR::installDepConda(gpu = FALSE)` if you have anaconda available.


For Windows user
- Ensure that you have Anaconda available.
- Install dependencies through `{r eval=FALSE} rlR::installDepConda(gpu = FALSE)` 

## Usage
```{r}
library(rlR)
listGymEnvs()[1L:10L]
env = makeGymEnv("CartPole-v1")
env$overview()
listAvailAgent(env)
```

```{r eval=TRUE}
conf = getDefaultConf("AgentFDQN")
conf$show()
conf$set(render = FALSE, console = FALSE)
```

```{r learn, eval=FALSE}
agent = makeAgent("AgentFDQN", env, conf)
perf = agent$learn(200L)
```

```{r mplot, eval=FALSE,fig.path="inst/figures/", warning=FALSE, message=FALSE}
perf$plot()
```
